%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.925]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Artem}{Aliev}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{Product Manager}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{909-839-3097}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
% \email{xpan1@swarthmore.edu}                               % optional, remove / comment the line if not wanted
% \homepage{shawnpan.me}                         % optional, remove / comment the line if not wanted
% \extrainfo{}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
\faLinkedin\enspace \href{https://www.linkedin.com/in/alievlin}{alievlin} &
\faGithub\enspace \href{https://github.com/alievgithub}{alievgithub} & \faEnvelopeO\enspace alievae0410@gmail.com &  \faMobile\enspace +7-964-585-6317

\end{tabular}
\end{center}

\section{SUMMARY}
\begin{minipage}{\maincolumnwidth}
\small Results-driven Product Manager with hands-on experience in IT Cloud Services (PaaS \& SaaS) product development and user engagement. Focused on improving key metrics including Retention, MAU, and Churn Rate while enhancing overall user satisfaction. Additional expertise in marketing, strategic \& research consulting.
\end{minipage}

\section{EXPERIENCE}
{\customcventry{October 2023 - Present (1 year 7 months)}{Product \& Marketing Manager}{1C Company}{Moscow, Russia}{}
{\begin{itemize}
\item Managed product roadmap and backlog, prioritizing features based on client needs and business goals.
\item Collaborated with clients to gather feedback and implement improvements, boosting satisfaction 30\% (based on surveys).
\item Presented at industry conferences on product monetization strategies, attracting new partners.
\item Developed analytics and marketing strategies for 1C:Enterprise.Element Technology, increasing user activity.
\item Created dashboards for user activity analysis, improving retention by 85\% in public beta.
\end{itemize}
}
}

{\customcventry{April 2023 - August 2023 (5 months)}{Strategy Research Analyst}{Department of Special Projects at the State Corporation}{Moscow, Russia}{}
{\begin{itemize}
\item Developed development strategies for the agro-industry and energy sectors of a Russian region.
\item Collaborated on the creation of ML models from scratch to predict economic performance up to 2035,\\ contributing to data analysis, task formulation, and interpretation of results.
\item Conducted media and regulatory monitoring on topics related to sustainable economic development.
\end{itemize}
}
}

{\customcventry{November 2022 - February 2023 (4 months)}{Strategy Consultant / Analyst}{BIC Group (ex. Roland Berger)}{Moscow, Russia}{}
{\begin{itemize}
\item Optimized business processes, reducing costs through reduction of the workforce by 4\% without loss of productivity.
\item Developed hypotheses for process reengineering, reducing task completion time by 12\%.
\end{itemize}
}
}

{\customcventry{October 2021 - September 2022 (1 year)}{Marketing Effectiveness Junior Consultant}{Nielsen Media}{Moscow, Russia}{}
{\begin{itemize}
\item Analyzed ROI of advertising campaigns, optimizing budgets and increasing effectiveness by 7\% under baseline sales.
\item Engaged in building regression models to forecast sales and improve marketing strategy planning.
\item Collaborated with international teams and clients in English, presenting findings and recommendations to stakeholders.
\end{itemize}
}
}

{\customcventry{April 2021 - July 2021 (4 months)}{HR Compensation \& Benefits Intern}{Sanofi}{Moscow, Russia}{}
{\begin{itemize}
\item Analyzed compensation and benefits data, creating dashboards in Excel.
\item Participated in tenders with insurance companies, optimizing VHI costs.
\end{itemize}
}
}

\section{SKILLS}
\begin{itemize}
\item \textbf{Product Management}: Product Discovery \& User Research, A/B Testing \& Experimentation, Data-Driven\\ Product Development, Agile Project Management, Stakeholder Collaboration \& Communication.
\item \textbf{Product Analytics}: Metrics Definition \& Analysis (ROI, Effectiveness et al.),
Business Process Design \& Optimization.
\item \textbf{Tools:} Excel, Word, PowerPoint, 1C:Analytics, 1C:Enterprise.Element, Jira, Confluence, Visio, Nielsen Answers.
\end{itemize}

\section{EDUCATION}
{\customcventry{2023 - 2025}{M.S.; Phystech School of AMCS; Business Informatics (GPA: 4.4/5.0)}{Moscow Institute of Physics and Technology}{Moscow, Russia}{}{}}
{\customcventry{2019 - 2023}{B.S.; Phystech School of ASTECH; System Analysis and Management (GPA: 4.2/5.0)}{Moscow Institute of Physics and Technology}{Moscow, Russia}{}{}}
{\customcventry{2019 - 2022}{Incomplete B.S.; Institute of EMIT; Economics (GPA: 4.0/5.0)}{The Russian Presidential Academy of National Economy and Public Administration}{Moscow, Russia}{}{}}

\section{UNIVERSITY TEAM PROJECTS}
{
  {\begin{itemize}
  \item \href{https://disk.yandex.com/d/EUMrDL89-MqzmQ}{Developed own app for Sprint progress reports on 1C:Enterprise.Element Technology.}
  \item \href{https://github.com/alievgithub/SpeechRecognitionBot}{Worked on speech recognition TG Bot for music track search using Python.}
  \end{itemize}
  }
}



% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
